---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```

# mcstprules

<!-- badges: start -->
<!-- badges: end -->

The goal of `mcstprules` is to provide a comprehensive set of tools to compute, analyze, and visualize cost allocation rules for Minimum Cost Spanning Tree Problems (MCSTP). The package implements algorithmic methods, rules based on cooperative game theory, and a robust suite of analytical tools.

<br>

## Installation

You can install the development version of `mcstprules` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("luciasouto13/mcstprules")
library(mcstprules)
```

<br>

## Features

The package organizes its functions into three main categories:


### Algorithmic Rules

These rules are derived directly from the network's structure and classic MST algorithms:

- Prim-Based: `mcstBird` (Bird) and `mcstDuttaKar` (Dutta-Kar).

- Kruskal-Based: `mcstFolk` (Folk/ERO), `mcstOWShapley` (Optimistic Weighted Shapley), and `mcstPWShapley` (Pessimistic Weighted Shapley).

- Other Approaches: `mcstBoruvka` (Boruvka) and `mcstCone` (Cone-wise Decomposition).


### Cooperative Games

These rules compute the Shapley value or the Nucleolus of cooperative games associated with the MCSTP:

- `mcstGamePrivate`: also known as the pessimistic game. Its Shapley value corresponds to Kar's rule (`mcstKar`).

- `mcstGameIrred`: based on the irreducible cost matrix.

- `mcstGameOpt`: optimistic game approach.

- `mcstGamePublic`: connections through agents are publicly available.

- `mcstGameCC`: based on the cycle-complete matrix.


### Analysis Tools

A comprehensive suite to evaluate stability and sensitivity:

- Core Stability & Geometry: `mcstCoreCheck`, `mcstCorePoints`, and `mcstCorePlot` to evaluate stability, find blocking coalitions, and visualize the core region.

- Sensitivity: `mcstStabilityRange` and `mcstSensitivity` to evaluate how cost variations affect optimal trees and cost allocations.

- Comparison: `mcstCompare` to simultaneously evaluate the main rules.

<br>

## Examples

The package is highly flexible and accepts network costs in multiple formats: square matrices, lower triangular vectors, edge lists, `igraph` objects, and even direct `.csv` or `.xlsx` file paths.

This basic example shows how to define a cost matrix and compute cost allocations for a 3-agent problem (where node 0 is the source):

```{r example}
library(mcstprules)

# Define a cost matrix for 3 agents + source (node 0)

# 1. Using an edge list format
costs <- data.frame(from = c(0, 0, 0, 1, 1, 2),
                    to   = c(1, 2, 3, 2, 3, 3),
                    cost = c(12, 15, 12, 4, 6, 8))

# 2. Using a square matrix
# costs <- matrix(c(0, 12, 15, 12,
#                  12,  0,  4,  6,
#                  15,  4,  0,  8,
#                  12,  6,  8,  0), nrow = 4, byrow = TRUE)

# 3. Using the lower triangular vector
# costs <- c(12, 15, 12, 4, 6, 8) 


# Algorithmic rules
mcstBird(costs)
mcstFolk(costs)

# Cooperative game theory rules
mcstKar(costs)
mcstGamePublic(costs, sol = "nucleolus")
```


### Comparing Rules

You can easily compare the standard allocation rules:

```{r}
mcstCompare(costs)
```


### Visualizing the problem

You can also visualize the network and the resulting allocation using the built-in plotting capabilities (based on the `igraph` package):

```{r plot, fig.alt = "Graphical representation of Bird's rule allocation"}
# Example plot for Bird's Rule
bird <- mcstBird(costs, draw = TRUE)
```

```{r plot_game, fig.alt = "Graphical representation of Kar's rule allocation"}
# Example plot for Private Game (Kar's rule)
kar <- mcstKar(costs, draw = TRUE)
```


### Advanced Analysis

`mcstprules` provides advanced tools to evaluate the stability, geometric properties, and sensitivity of the computed rules:

```{r}
# Core Stability Check
mcstCoreCheck(game = mcstGamePrivate(costs))
```

```{r plot_core, fig.alt = "Graphical representation of the core", fig.width = 5.75, fig.height = 5.75}
# Core Emptiness
core <- mcstCorePoints(game = mcstGamePrivate(costs)); core
plot(core)
```

```{r plot_sens, fig.alt = "Sensitivity analysis for arc 1-3"}
# Sensitivity Analysis
sens <- mcstSensitivity(costs, rule = "bird", arcs = c(1, 3))
plot(sens)
```


## Documentation

You can also download the [full PDF manual here](mcstprules_0.1.0.pdf).
