---
title: "Algorithmic Cost-Sharing Rules for MCST Problems"
author: "Lucía Souto Vázquez"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Algorithmic Cost-Sharing Rules for MCST Problems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This vignette introduces the algorithmic cost-sharing rules implemented in the `mcstprules` package. These rules allocate costs based on procedures derived directly from the construction of minimum cost spanning trees.

## Problem Setting

We consider a Minimum Cost Spanning Tree Problem (MCSTP) where a set of agents must be connected to a common source at minimum total cost.

## Getting Started

First, define a cost matrix where the first row/column represents the source (node 0).

```{r setup}
library(mcstprules)

# Example: a 3-agent cost matrix
costs <- matrix(c(0, 12, 15, 12, 
                 12,  0,  4,  6, 
                 15,  4,  0,  8, 
                 12,  6,  8,  0), nrow = 4, byrow = TRUE)
```

## Implemented Rules

(This section will describe the available rules.)

## Remarks

(Additional notes and comparisons will be included here.)

